\documentclass[a4paper,11pt]{article}
\usepackage[a4paper]{geometry}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{float}

\input{EternalWebclassdiagram}
\input{TUPTclassdiagram}

\title{[P2PBrowser group] Code Architechture}
\author{Steffan Norberhuis \and Quinten Stokkink}
\date{12 June 2013}
\begin{document}
   \maketitle

\section{Introduction}
Our projects consists of two seperate extensions of Tribler. Both use wxWebview to browse the internet.
The first extension is the Eternal Webpage extension.
This extension will allow a user to easily browse the web using peer-to-peer-swarms and also add new pages to the swarm.
The second extension is the TUPT extension.
This extension allows you to browse websites and if a movie is detected on the website,
then you can begin streaming this movie with one click of a button.

The only common part between the two extensions is the WebBrowser class.
After we finished the Eternal Webpages extension, we started working on the TUPT extension.
We transformed the WebBrowser class and stripped all functionality specific for the EternalWebpages extension that was no longer needed.
All needed functionality for the TUPT extension to the WebBrowser class has been added in a generic way.
This generic approach was much harder for the WebBrowser, because we changed the way how WebBrowser loads pages.

The projects use Python 2.7 and are compiled as part of the Tribler project (see \url{https://github.com/Tribler/tribler}).
Because we cannot/should not deliver code that is not our own we have ripped out our code
from the main Tribler code. The result of this move is that the project is uncompilable and 
some of the tests unrunnable. This should not really be of any hindrance to evaluating the code though.

\section{Eternal Webpages diagrams}
\input{siteripperdiagrams}

\section{TUPT diagrams}
\input{tuptdiagrams}

\section{Tests}
\input{tests}

\end{document}
